---
title: "Bitcoin Mining - Backtest and Predictions"
output: rmarkdown::github_document
---

This project consists of two sub-parts:

- Bitcoin mining - historical backtest example.
- Bitcoin mining - Future profitability predictions (based on trend regressions).

# Historical Backtest

Assumptions:

- Five antminer S9 ASIC Miners bought at 2300 USD per miner in july 2016. 
- Energy efficient mining in Iceland at 5 cents per kwh. 
- Initial 500USD operational expense (shipping, setup costs, etc..).

Relevant network data and mining results are illustrated below.


```{r message=FALSE}
source("config/Config.R")

BitcoinMiningBacktest(miner.price    = 2300,
                      fixed.cost     = 500,
                      miner.power    = 1247,
                      miner.hashrate = 13, 
                      nr.miners      = 5,
                      cost.kwh       = 0.05,
                      cost.var.daily = 0,
                      backtest.start = "2016-07-01")
```

# Future Profitability Predictions

The ```BitcoinMiningBacktest``` expects future bitcoin price predictions, total network hashrate predictions and total network revenue predictions as input when it's run in ```forward.mode```.

Assumptions:

- Use exponential regression to predict the bitcoin price trend.
- Use exponential regression to predict the total network revenue trend.
- Use loess regression with degree 1 to predict the future hashrate trend.
- Miners sell at around 1288 per unit.
- Predict up to 500 days ahead.
- Other assumptions are the same as before.

The section below illustrates the results of the individual trend regressions followed by the mining profitability forward simulation (using the predicted trendvalues as input).

### Bitcoin Price (Exponential Regression)

```{r message=FALSE}
date.start <- "2011-01-01"
btc.price <- FetchBTCInfo(param           = "market-price",   
                          data.identifier = "btc.close", 
                          date.start      = date.start)

btc.predictions <- SimpleLogTrendRegression(data = btc.price, 
                                            data.identifier = "BTC-price", 
                                            regression.type = "exponential",
                                            data.frequency  = "daily",
                                            nr.future       = 500, 
                                            plot.2sd.log    = TRUE, 
                                            plot.2sd.levels = FALSE)
```

### Total Network Mining Revenue (Exponential Regression)

```{r message=FALSE}
## Total network mining revenue (coinbase + transaction) - Exponential regression.
mining.revenue.usd <- FetchBTCInfo(param           = "miners-revenue", 
                                   data.identifier = "mining.revenue",
                                   date.start      = date.start)

revenue.predictions <- SimpleLogTrendRegression(data = mining.revenue.usd, 
                                            data.identifier = "Mining.Revenue", 
                                            regression.type = "exponential",
                                            data.frequency  = "daily",
                                            nr.future       = 500, 
                                            plot.2sd.log    = TRUE, 
                                            plot.2sd.levels = FALSE)
```


### Total Network Hashrate (Loess Regression)
```{r message=FALSE}
# Hashrate trend predictions (Loess, degree = 1)
hashrate.total <- FetchBTCInfo(param           = "hash-rate", 
                               data.identifier = "mining.hashrate",
                               date.start      = date.start)

hashrate.predictions <- SimpleLogTrendRegression(data = hashrate.total, 
                                                 data.identifier = "Network Hashrate",
                                                 regression.type = "loess",
                                                 data.frequency  = "daily",
                                                 loess.degree    = 1,
                                                 nr.future       = 500, 
                                                 plot.2sd.log    = TRUE, 
                                                 plot.2sd.levels = FALSE)
```


### Mining Profitability Simulation

```{r message=FALSE}
BitcoinMiningBacktest(miner.price     = 1288,
                      fixed.cost      = 500,
                      miner.power     = 1247,
                      miner.hashrate  = 13,
                      nr.miners       = 5,
                      cost.kwh        = 0.05,
                      cost.var.daily  = 0,
                      forward.mode    = TRUE,
                      bitcoin.price.predictions   = btc.predictions$level.trend,
                      network.revenue.predictions = revenue.predictions$level.trend,
                      network.hashrate.predictions = hashrate.predictions$level.trend)
```

## Donations

If you find this software useful and/or you would like to see additional extensions, feel free to donate some crypto:

 - BTC: 1QHtZLZ15Cmj4FPr5h5exDjYciBDhh7mzA
 - LTC: LhKf6MQ7LY1k8YMaAq9z3APz8kVyFX3L2M
 - ETH: 0x8E44D7C96896f2e0Cd5a6CC1A2e6a3716B85B479
 - DASH: Xvicgp3ga3sczHtLqt3ekt7fQ62G9KaKNB

Or preferably, donate some of my favorite coins :)

 - GAME: GMxcsDAaHCBkLnN42Fs9Dy1fpDiLNxSKX1
 - WAVES: 3PQ8KFdw2nWxQATsXQj8NJvSa1VhBcKePaf
 
## Licensing

Copyright 2017 Essential Data Science Consulting ltd. ([EssentialQuant.com](http://essentialquant.com "EssentialQuant") / jellenvermeir@essentialquant.com).
This software is copyrighted under the MIT license: View added [LICENSE](./LICENSE) file.
